Blocking-resistant communication\\through domain fronting

### 2014-12-21 docs/meek.tex
done with edit pass for lower-level tweaks/comments

The key idea of domain fronting is the use of
different domain names at different layers of communication.
In an HTTPS request, the destination domain name appears
in three places relevant to the discussion:
in the DNS query,
in the TLS Server Name Indication (SNI) extension~\cite[Section~3]{rfc6066},
and in the HTTP Host header~\cite[Section~14.23]{rfc2616}.
Usually, the same domain name appears in all three places.
In a domain-fronted request, however,
the DNS query and SNI carry one name (the ``front domain''),
while the HTTP Host header,
which is hidden from the censor by HTTPS encryption,
carries another (the actual destination).

@@

As an encrypted tunneling protocol, meek necessarily adds overhead.
Each chunk of data gets an HTTP header, and then the HTTP
request is wrapped in TLS.
We estimate the overhead when meek is used to transport Tor.
Tor uses fixed-size cells of 514 bytes~\cite[Section~0.2]{tor-spec}.
Each cell is wrapped in a TLS Application Data record, which adds 29 bytes
when using a GCM ciphersuite (the default in current versions of Tor).
% (in Tor version~0.2.4.22 using a GCM ciphersuite).
This 543-byte record is received by \meekclient,
which adds an HTTP header whose length is about 400 bytes
\vp{yikes, that's a lot of overhead $\ldots$}
(varying slightly depending on the length of the Host
\vp{It would help to put textual protocol elements in another typeface,
such as \texttt{Host}; you could define a backslash-header macro for this}
field).
The HTTP request goes into its own TLS Application Data record when it becomes HTTPS,
adding about 50~bytes
depending on how much padding is used by the ciphersuite in use.

@@

Domain fronting defeats address-based blocking and active probing.
HTTPS foils simple DPI,
hiding any byte patterns in the underlying stream.
The censor may also apply DPI to the tunnel itself in order to try to
distinguish fronted from non-fronted traffic.
This section is about TLS fingerprinting,
which is the censor's remaining easy distinguisher,
and how we use a web browser with an unremarkable TLS fingerprint
to disguise the HTTPS tunnel.
Section~\ref{sec:trafficanalysis} is about more subtle and hard-to-apply forms of traffic analysis.

The TLS handshake is largely plaintext~\cite[Section~7.4]{rfc5246}, and leaves
enough room for variation, for example in
the client's lists of ciphersuites and extensions,
that it is possible to fingerprint different client TLS implementations~\cite{ssl-p0f}
based on their handshake.
(We are only concerned with fingerprinting the client,
because the server's TLS
comes from the intermediate web service;
i.e., it is what you would expect to see when connecting to the front domain.)
Tor itself was blocked by China in 2011
because of the distinctive ciphersuite list it used at that time~\cite{bug4744}.
Figure~\ref{fig:ciphersuites} in Appendix~\ref{sec:ciphersuites} shows examples of how TLS client
implementations may detectably differ.
\meekclient is written in the Go programming language,
which has a custom TLS library~\cite{golang-crypto/tls};
Figure~\ref{fig:ciphersuites:golang}
shows how it would appear on the network with no TLS camouflage.
Figures~\ref{fig:ciphersuites:firefox} and~\ref{fig:ciphersuites:chrome}
show two browsers which have TLS fingerprints different from Go's
and different from each other's.
A censor could block an uncamouflaged \meek\ using Go's TLS fingerprint,
if it considered the collateral damage resulting from blocking other Go programs to be slight enough.

In order to disguise its TLS fingerprint,
\meekclient proxies all its HTTPS requests through an actual web browser.
We implemented extensions for two web browsers,
Firefox and Chrome,
that enable them to make HTTPS requests on behalf of \meekclient.
The TLS fingerprint looks like that of a browser, because it is that of a browser.
The browser instance running the extension is completely separate
from the browser the user interacts with.
It runs invisibly in the background in a separate process,
does not display a user interface,
and shares no state with the user's browser.

@@

Appropriate TLS camouflage may differ depending on circumstances.
On a traditional desktop PC, using a browser is probably the right choice.
When
[blinded circumvention tool]
% ANON
% Psiphon
ported \meekclient to Android,
they did not use a browser as camouflage,
but rather made all HTTPS requests with the standard Android HTTP API.
This decision makes sense because other Android applications
also use the standard API and share the same TLS fingerprint.

\section{A survey of fronting-capable\\web services}
\label{sec:survey}

This section contains a brief survey of fronting-capable
web services we have found, each with its pros and cons.
The list is not exhaustive and is meant to illustrate the broad
support for fronting that exists.
Of the services listed, we have so far deployed \meek\
only on Google App Engine and Amazon CloudFront.
For the others, we have only checked that fronting works.
Recall that even web services that support fronting
will front only for their own customers,
so new each deployment typically requires an investment of time and money.

Google App Engine~\cite{googleappengine}
is a web application platform.
Each application gets a user-specified subdomain of \urll{appspot.com},
which can be fronted through almost any Google domain,
including google.com, gmail.com, googleapis.com, and many others.
App Engine can run only web applications,
not a full Tor bridge;
for that reason we use a tiny ``reflector'' application
that merely copies incoming requests to a Tor bridge hosted elsewhere.
Fronting through App Engine is attractive in the case where
\urll{appspot.com} is blocked---not unlikely,
because of the ease of building a proxy there---but
at least one other Google service is reachable.
Applications that use less than one gigabyte of bandwidth daily
are free of charge,
making possible an upload-your-own-app model
à la GoAgent.

Amazon CloudFront~\cite{cloudfront},
not to be confused with CloudFlare,
is the CDN of Amazon Web Services.
A CloudFront ``distribution'' associates
an automatically generated subdomain of \urll{cloudfront.net}
with an origin server,
which in our case is an instance of \meekserver.
The front domain may be any other of CloudFront's automatically generated subdomains, all
of which support HTTPS through a wildcard certificate.
CloudFront has a usage tier that is free of charge for a year,
subject to a bandwidth limit of 50 gigabytes per month.

Microsoft Azure~\cite{azure}
is a cloud computing platform that features a CDN.
Similarly to CloudFront, users get automatically generated subdomains
of \urll{vo.msecnd.net},
all of which can front for each other.
The CDN works only for Azure domains, however,
so as with App Engine, it is necessary to run a trivial reflector app
that merely forwards requests out of Azure toward an external proxy.
There are other front domain names, like \urll{ajax.aspnetcdn.com},
that may offer high collateral damage.

CloudFlare~\cite{cloudflare},
not to be confused with CloudFront,
is a CDN also marketed as protection against
denial-of-service attacks.
It appears that any domain name on CloudFlare
can front for any other, even custom user-selected domains;
however it is not obvious which one is best to use as a front.
The front domain needs to be a popular one
(causing high collateral damage if blocked),
or the censor may simply block it entirely.
It is doubly bad when a domain is blocked in this way,
because not only is circumvention foiled,
but some unsuspecting third party has just had their web site blocked.
A solution may be to round-robin through
a pool of popular domain names;
or to use ``domainless'' fronting that does not send SNI.
% Though CloudFlare supports domain fronting,
% its terms of service~\cite{cloudflare-terms}
% seem to prohibit the kind of tunneled proxying that \meek\ does:
% \begin{quote}
% \textsc{Section 10: Limitation on non-HTML caching}\\
% You acknowledge that CloudFlare's Service is offered as a platform to cache and
% serve web pages and websites and is not offered for other purposes
% \ldots\ you understand and agree to use the Service solely
% for the purpose of hosting and serving web pages\ldots
% \end{quote}

@@

Fastly~\cite{fastly} is a CDN.
It is the only one of the services we tested in that
that appears to enforce SNI:
if the SNI and Host do not match,
the Fastly edge server returns an HTTP 400 (``Bad Request'') error.
However, if the TLS ClientHello omits SNI, then the Host may be any Fastly domain.
It is the only service we have found
that requires the ``domainless'' fronting style.

@@

One of our goals in developing \meek\ is to force
the censor to use relatively more expensive statistical classifiers
to effect blocking---generally, to increase the cost of censorship.
We believe \meek\ is resistant to the ``easy''
forms of blocking, namely IP address and DNS blocking,
simple pattern-based DPI,
and active probing.
We hope to force the censor to resort to measuring
more subtle features of the communication.
In this section we provide a preliminary analysis
of \meek's resistance to such attacks.
Specifically, we consider three traffic features:
packet length distribution,
number of simultaneous connections,
and connection lifetime.

@@

% Advantage is that we are probably proxying web traffic.
As \meek\ is based on HTTPS,
we compare traffic traces of \meek\ against
traces of ``ordinary'' HTTPS traffic.
We did a packet capture
of automatically browsing the home pages
of the top 500 Alexa web sites using \meek\ in Tor Browser,
with the browser camouflage described in Section~\ref{sec:browserextension},
and Google App Engine as the intermediate web service.
The \meek\ trace is 687~megabytes in all
and covers about 4.5 hours of network activity.
Our representative of ordinary HTTPS traffic
is a sanitized 10-minute trace
from 
%Lawrence Berkeley National Laboratory (\lbl)
a research lab [blinded as \lbl for anonymous submission],
comprising data to and from TCP port 443 on any Google server.
% Mention the non-google if it appears in a figure.
The \lbl trace consists 313~megabytes of packet headers,
not payloads, destined for TCP port 443 on any Google server.
The original IP addresses were masked by being
replaced by a counter before we received the trace.

@@

We consider the duration of TCP connections as a potential distinguisher.
Figure~\ref{fig:duration} shows the cumulative probability
of connection durations in our two traces.
Considering the \lbl trace first,
we see interesting probability concentrations on
round numbers: 10~s, 60~s, 120~s, 180~s, and 240~s.
We hypothesize that this phenomenon is caused by
keepalive timeouts in web browsers and servers,
and polling behavior of web apps.
The small rise at 600 seconds is an artifact caused
by the fact that the trace is only 10 minutes long.
Connections lasting longer than 10 minutes are not accurately reflected,
however we can say that only about 8\% of connections lasted longer than 10 minutes.

@@

In light of these findings,
the censor may decide to block any long-lived HTTPS connections between
a client and a web service.
According to our traffic trace, doing so will not disrupt more than 8\% of ordinary connections;
whether that is an acceptable cost depends on the time threshold and the censor's
tolerance for collateral damage.
The censor can lower the timing threshold, at the cost of more false positives.
Duration-based blocking is favorable for the circumventor,
because if the censor terminates connections after, say, 10 minutes,
in any case that's 10 minutes of circumvention achieved,
after which \meek\ can start a new connection
and allow Tor to rebuild its circuits.
Future enhancements in \meek\ may even allow reconnecting using the same session ID,
so there will be no effect on the client other than a brief delay
while a new HTTPS connection is established.

@@

\begin{figure}
\centering
\includegraphics[width=\linewidth]{concurrent.pdf}
\caption{
Number of simultaneous HTTPS connections to any Google server.
Each pale line indicates the number of HTTPS connections
of a single client IP address.
The \lbl trace shows 2,745 unique clients and the \meek\ trace only one.
The dark line is a smoothed average number of connections per client.
The \meek\ count stays close to~1 throughout, only momentarily
jumping to 0 or~2.
The average number of connections per user in the \lbl trace is 2.61,
and in the \meek\ trace is 1.002.
}
\label{fig:concurrent}
\end{figure}

The number of concurrent connections is another potential distinguisher.
We have seen how \meek\ tends to use one long-lived connection
through which it tunnels all its requests.
Figure~\ref{fig:concurrent} compares the number of concurrent HTTPS connections to
Google per client in both traces.
The number of connections in the \lbl trace is variable,
with some hosts briefly spiking up above 50 connections,
but the average case is very heavily skewed to smaller numbers.
The average number of connections in the \lbl trace is 2.61,
with 28\% of clients never having more than 2 concurrent connections.
In the \meek trace the average is almost exactly 1, only briefly
deviating when one connection ends and another begins.
We conclude that having a small number of concurrent connections is unremarkable.

@@

For the purposes of censorship circumvention,
one does not need to match exactly a ``typical'' traffic profile;
only not to deviate from it too much.
Circumvention traffic must only be difficult enough to distinguish from ordinary traffic
that blocking it requires an amount of false positives unacceptable to the censor.
Even 1\% of Google traffic accidentally blocked may exceed the collateral damage tolerance of some censors.
Further, it is hard to characterize what normal use is of, say, a CDN:
they provide access to ordinary web sites,
but also to video streams and software updates,
and not all clients are web browsers.
The difficulty we face is symmetric;
if finding the right model is difficult task for us,
it is also difficult for the censor.
We have seen that censors prefer to use easy classifiers when they exist.
By removing the easy ways, we increase the censor's cost.

@@

Development on \meek\ as a Tor pluggable transport~\cite{pt} began in January~2014.
Our target for deployment is Tor Browser~\cite{torbrowser},
a customized version of Firefox that is
preconfigured to use a built-in Tor client.
% and patched to defend against application-layer privacy and anonymity threats
% like tracking cookies and web browser fingerprinting.
Tor Browser has an easy interface for selecting pluggable transports.
% ANON
% [Some details of deployment are omitted for anonymous submission.]
% We made a series of experimental releases of Tor Browser featuring \meek,
% releasing the first one on February~18.
% On April~18 we made the first release featuring the browser camouflage
% that is the subject of Section~\ref{sec:browserextension}.
% We announced our releases on Tor development mailing lists,
% whence they were picked up by Tor Weekly News on the Tor blog.
% Our code was merged by the Tor Browser maintainers
% in June and is scheduled for an alpha release,
% still pending as of this writing.

We have so far deployed on three backends:
Google App Engine,
Amazon CloudFront,
and Microsoft Azure.
Figure~\ref{fig:clients-tor} shows the daily average number of concurrent users of \meek.
(A measurement of 500, for example, means that there were on average 500
users of the system at any given time during the day.)
The App Engine backend was established in February;
CloudFront in July;
and Azure in October.
Also in Figure~\ref{fig:clients-tor} is a table of monthly costs for each web service.
The pricing for cloud services is complicated,
depending not only on bandwidth but also on geographical region and other factors.
For example CloudFront charges per request as well as per gigabyte,
and about 54\% of the CloudFront bill for October was for requests.
App Engine charges extra when it has to run multiple instances
of an app's code to cope with load;
about 15\% of October's App Engine bill was for such ``instance hours.''
% These and other cost details are summarized in a mailing list post~\cite{meek-costs-201410}.
The App Engine and CloudFront backends are running on accounts
that provide a limited amount of free bandwidth,
but current use greatly exceeds the free thresholds.
Azure service is being donated and so has not yet cost anything.
The total cost so far has been \$187.13,
but this number is expected to more than double in November and continue to increase.

\begin{figure}
\centering
\includegraphics[width=\linewidth]{clients-meek}
\begin{tabular}{l r r r}
       &App Engine &CloudFront&  Azure \\
\hline
Jan--Jul &  \$2.72 &   \$0.00 & \$0.00 \\
Aug      &  \$1.56 &   \$3.10 & \$0.00 \\
Sep      &  \$4.02 &   \$4.59 & \$0.00 \\
Oct      & \$40.85 & \$130.29 & \$0.00 \\
\hline
total    & \$49.15 & \$137.98 & \$0.00 \\
\end{tabular}
\caption{
Concurrent users of the \meek\ pluggable transport
and month-by-month operational costs.
The total cost to date is \$187.13.
% ANON
% The large increase of users on October~15 coincides with
% the release of Tor Browser~4.0,
% the first release to make meek easily available.
Azure CDN service is currently being donated as part of a research grant.
The user estimates come from the Tor Metrics Portal~\cite{metrics-meek,counting-daily-bridge-users}.
}
\label{fig:clients-tor}
\end{figure}

@@

Domain fronting derives its strength from the
high collateral damage of blocking the fronted-through domain.
To front through \urll{www.google.com} to App Engine, for example,
is to make a bet that the censor will lack the temerity to block Google.
Different censors will differ in their aversion to collateral damage;
blocking an important service is a costly measure
that harms users not involved in circumvention and perhaps a society's economic well-being,
and not all censors can afford to do it.
The Great Firewall of China took the unprecedented step
of blocking all Google services in June 2014~\cite{cn-google-block,cn-google-block-greatfire},
and has since blocked certain CDN domains that were used to host
mirrors of censored web sites, even at the cost of damaging other unrelated sites~\cite{cn-edgecast-block-greatfire}.
In 2012, the government of Pakistan blocked all of YouTube
in order to restrict access to one video,
and in 2011, the government of Egypt briefly completely ``turned off the net.''
% http://www.washingtonpost.com/business/economy/youtube-blocked-in-pakistan/2012/09/17/30081fa2-00ea-11e2-b257-e1c2b3548a4a_story.html
% https://en.wikipedia.org/wiki/Internet_censorship_in_Egypt#2011_Internet_shutdown
These examples show that blocking resistance is not an absolute,
black-and-white security property;
it can only be discussed in an economic context, relative to the costs borne
by the censor and by users of a system.
We can at least roughly quantify the cost of blocking a domain-fronting system:
it is the minimum cost of
blocking the front domain with resultant collateral damage,
conducting a traffic-analysis attack to distinguish
circumvention from ordinary traffic, or
conducting some other unconsidered attack, for example physical surveillance of Internet users.
As long as all these costs are high,
domain fronting is difficult to block.

>>>>

The key idea of domain fronting is the use of
different domain names at different layers of communication.
In an HTTPS request, the destination domain name appears
in three places relevant to the discussion:
in the DNS query,
in the TLS Server Name Indication (SNI) extension~\cite[\S 3]{rfc6066},
and in the HTTP Host header~\cite[\S 14.23]{rfc2616}.
Usually, the same domain name appears in all three places.
In a domain-fronted request, however,
the DNS query and SNI carry one name (the ``front domain''),
while the HTTP Host header,
which is hidden from the censor by HTTPS encryption,
carries another (the actual destination).

@@

As an encrypted tunneling protocol, meek necessarily adds overhead.
Each chunk of data gets an HTTP header, and then the HTTP
request is wrapped in TLS.
We estimate the overhead when meek is used to transport Tor.
Tor uses fixed-size cells of 514 bytes~\cite[\S 0.2]{tor-spec}.
Each cell is wrapped in a TLS Application Data record, which adds 29 bytes
when using a GCM ciphersuite (the default in current versions of Tor).
% (in Tor version~0.2.4.22 using a GCM ciphersuite).
This 543-byte record is received by \meekclient,
which adds an HTTP header whose length is about 400 bytes
\vp{yikes, that's a lot of overhead $\ldots$}
(varying slightly depending on the length of the Host
\vp{It would help to put textual protocol elements in another typeface,
such as \texttt{Host}; you could define a backslash-header macro for this}
field).
The HTTP request goes into its own TLS Application Data record when it becomes HTTPS,
adding about 50~bytes
depending on how much padding is used by the ciphersuite in use.

@@

Domain fronting defeats address-based blocking and active probing.
HTTPS foils simple DPI,
hiding any byte patterns in the underlying stream.
The censor may also apply DPI to the tunnel itself in order to try to
distinguish fronted from non-fronted traffic.
In this section we discuss addressing the problem of TLS fingerprinting,
which is the censor's remaining easy distinguisher.
We so by using a web browser with an unremarkable TLS fingerprint
to disguise the HTTPS tunnel.
Section~\ref{sec:trafficanalysis} analyzes
more subtle and hard-to-apply forms of traffic analysis.

The TLS handshake is largely plaintext~\cite[\S7.4]{rfc5246}, and leaves
enough room for variation, for example in
the client's lists of ciphersuites and extensions,
that it is possible to fingerprint different client TLS implementations~\cite{ssl-p0f}
based on their handshake.
(We are only concerned with fingerprinting the client,
because the server's TLS
comes from the intermediate web service;
i.e., it is what you would expect to see when connecting to the front domain.)
Tor itself was blocked by China in 2011
because of the distinctive ciphersuite list it used at that time~\cite{bug4744}.
Figure~\ref{fig:ciphersuites} in Appendix~\ref{sec:ciphersuites} shows examples of how TLS client
implementations may detectably differ.
\meekclient is written in the Go programming language,
which has a custom TLS library~\cite{golang-crypto/tls};
Figure~\ref{fig:ciphersuites:golang}
shows how it would appear on the network with no TLS camouflage.
Figures~\ref{fig:ciphersuites:firefox} and~\ref{fig:ciphersuites:chrome}
show two browsers which have TLS fingerprints different from Go's
and different from each other's.
A censor could block an uncamouflaged \meek\ using Go's TLS fingerprint,
if it considered the collateral damage resulting from blocking other Go programs to be slight enough.

In order to disguise its TLS fingerprint,
\meekclient proxies all its HTTPS requests through an actual web browser.
We implemented extensions for two web browsers,
Firefox and Chrome,
that enable them to make HTTPS requests on behalf of \meekclient.
The TLS fingerprint looks like that of a browser, because it is that of a browser.
The browser instance running the extension is completely separate
from the browser the user interacts with.
It runs invisibly in the background in a separate process,
does not display a user interface,
and shares no state with the user's browser.
\vp{Would be helpful to discuss what sort of overhead this incurs}

@@

Appropriate TLS camouflage may differ depending on circumstances.
On a traditional desktop PC, using a browser is probably the right choice.
When
[blinded circumvention tool]
\vp{does this need to be blinded?}
% ANON
% Psiphon
ported \meekclient to Android,
they did not use a browser as camouflage,
but rather made all HTTPS requests with the standard Android HTTP API.
This decision makes sense because other Android applications
also use the standard API and share the same TLS fingerprint.

\section{A survey of fronting-capable web services}
\label{sec:survey}

\vp{This whole section should be beefed up with a deeper assessment.  Along
these lines, it would help to include a summary table.}
This section contains a brief survey of fronting-capable
web services we have found, each with its pros and cons.
The list is not exhaustive and is meant to illustrate the broad
support for fronting that exists.
Of the services listed, we have so far deployed \meek\
only on Google App Engine and Amazon CloudFront.
For the others, we have only checked that fronting works.
Recall that even web services that support fronting
will front only for their own customers,
so new each deployment typically requires an investment of time and money.

Google App Engine~\cite{googleappengine}
is a web application platform.
Each application gets a user-specified subdomain of \urll{appspot.com},
which can be fronted through almost any Google domain,
including google.com, gmail.com, googleapis.com, and many others.
App Engine can run only web applications,
not a full Tor bridge;
for that reason we use a tiny ``reflector'' application
that merely copies incoming requests to a Tor bridge hosted elsewhere.
Fronting through App Engine is attractive in the case where even though
the censor blocks
\urll{appspot.com}---which could well occur,
because of the ease of building a proxy there---at least one
other Google service remains reachable.
Applications that use $< 1$~GB of bandwidth daily
are free of charge,
making possible an upload-your-own-app model
à la GoAgent.

Amazon CloudFront~\cite{cloudfront}
(not to be confused with CloudFlare; see below)
is the CDN of Amazon Web Services.
A CloudFront ``distribution'' associates
an automatically generated subdomain of \urll{cloudfront.net}
with an origin server,
which in our case is an instance of \meekserver.
The front domain may be any other of CloudFront's automatically generated subdomains, all
of which support HTTPS through a wildcard certificate.
CloudFront has a usage tier that is free of charge for a year,
subject to a bandwidth limit of 50~GB/month.

Microsoft Azure~\cite{azure}
is a cloud computing platform that features a CDN.
Similarly to CloudFront, users get automatically generated subdomains
of \urll{vo.msecnd.net},
all of which can front for each other.
The CDN works only for Azure domains, however,
so as with App Engine, it is necessary to run a trivial reflector app
that merely forwards requests out of Azure toward an external proxy.
There are other front domain names, like \urll{ajax.aspnetcdn.com},
that may provide entangling with high collateral damage.

CloudFlare~\cite{cloudflare}
is a CDN also marketed as protection against
denial-of-service attacks.
It appears that any domain name on CloudFlare
can front for any other, even custom user-selected domains;
however it is not obvious which one is best to use as a front.
The front domain needs to be a popular one
(causing high collateral damage if blocked),
or the censor may simply block it entirely.
It is doubly bad when a domain is blocked in this way,
because not only is circumvention foiled,
but some unsuspecting third party has just had their web site blocked.
A solution may be to round-robin through
a pool of popular domain names;
or to use ``domainless'' fronting that does not send SNI.
\vp{Would be quite valuable to more broadly assess the viability
of using domainless fronting}
% Though CloudFlare supports domain fronting,
% its terms of service~\cite{cloudflare-terms}
% seem to prohibit the kind of tunneled proxying that \meek\ does:
% \begin{quote}
% \textsc{Section 10: Limitation on non-HTML caching}\\
% You acknowledge that CloudFlare's Service is offered as a platform to cache and
% serve web pages and websites and is not offered for other purposes
% \ldots\ you understand and agree to use the Service solely
% for the purpose of hosting and serving web pages\ldots
% \end{quote}

@@

Fastly~\cite{fastly} is a CDN.
It is the only one of the services we tested that
appears to enforce SNI consistency:
if the SNI and Host do not match,
the Fastly edge server returns an HTTP 400 (``Bad Request'') error.
However, if the TLS ClientHello omits SNI, then the Host may be any Fastly domain.
It is the only service we have found
that requires the ``domainless'' fronting style.

@@

One of our goals in developing \meek\ is to force
the censor to use relatively more expensive statistical classifiers
to effect blocking---generally, to increase the cost of censorship.
We believe \meek\ is resistant to the ``easy''
forms of blocking, namely IP address and DNS blocking,
simple pattern-based DPI,
and active probing.
\vp{sketch for the reader why it's resistant to active probing}
We hope to force the censor to resort to measuring
more subtle features of the communication.
In this section we provide a preliminary analysis
of \meek's resistance to such attacks.
Specifically, we consider three traffic features:
packet length distribution,
number of simultaneous connections,
and connection lifetime.

@@

% Advantage is that we are probably proxying web traffic.
As \meek\ is based on HTTPS,
we compare traffic traces of \meek\ against
traces of ``ordinary'' HTTPS traffic.
We did a packet capture
of automatically browsing the home pages
of the top 500 Alexa web sites using \meek\ in Tor Browser,
with the browser camouflage described in Section~\ref{sec:browserextension},
and Google App Engine as the intermediate web service.
The \meek\ trace is 687~MB
and spans 4.5~hours of network activity.
Our representative of ordinary HTTPS traffic
is a sanitized 10-minute trace
from 
%Lawrence Berkeley National Laboratory (\lbl)
a large ($\approx$~4K~users)
research lab [blinded as \lbl for anonymous submission],
comprising data to and from TCP port 443 on any Google server.
% Mention the non-google if it appears in a figure.
The \lbl trace consists 313~MB of packet headers,
not payloads, destined for TCP port 443 on any Google server.
The original IP addresses were masked by being
replaced by a counter before we analyzed the trace.

@@

We consider the duration of TCP connections as a potential distinguisher.
Figure~\ref{fig:duration} shows the cumulative probability
of connection durations in our two traces.
Considering the \lbl trace first,
we see interesting probability concentrations on
round numbers: 10/60/120/180/240~seconds.
We hypothesize that this phenomenon is caused by
keepalive timeouts in web browsers and servers,
and polling behavior of web apps.
The small rise at 600 seconds is an artifact caused
by the fact that the trace is only 10 minutes long.
Connections lasting longer than 10 minutes are not accurately reflected,
however we can say that only about 8\% of connections lasted longer than 10 minutes.

@@

In light of these findings,
the censor may decide to block any long-lived HTTPS connections between
a client and a web service.
According to our traffic trace, doing so will not disrupt more than 8\% of ordinary connections;
\vp{It could though disrupt valuable large transfers, which might be quite
important}
whether that is an acceptable cost depends on the time threshold and the censor's
tolerance for collateral damage.
The censor can lower the timing threshold, at the cost of more false positives.
Duration-based blocking is favorable for the circumventor,
because if the censor terminates connections after, say, 10~minutes,
in any case that represents 10~minutes of circumvention achieved,
after which \meek\ can start a new connection
\vp{well, it can't start a new connection if the censor's response is to block
the client}
and allow Tor to rebuild its circuits.
Future enhancements in \meek\ may even allow reconnecting using the same session ID,
so there will be no effect on the client other than a brief delay
\vp{couldn't you eliminate this by building the new circuit concurrently?
that won't work if the censor blocks by IP rather than by connection;
but you have that problem anyway particularly if the censor blocks the
client rather than, or in addition to, the server}
while a new HTTPS connection is established.

@@

\begin{figure}
\centering
\includegraphics[width=\linewidth]{concurrent.pdf}
\caption{
Number of simultaneous HTTPS connections to any Google server.
Each pale line indicates the number of HTTPS connections
of a single client IP address.
\vp{Not clear what consitutes a ``pale line''.  Try to ensure this
works when printed in black-and-white.}
The \lbl trace shows 2,745 unique clients and the \meek\ trace only one.
The dark line is a smoothed average number of connections per client.
The \meek\ count stays close to~1 throughout, only momentarily
jumping to 0 or~2.
The average number of connections per user in the \lbl trace is 2.61,
and in the \meek\ trace is 1.002.
}
\label{fig:concurrent}
\end{figure}

The number of concurrent connections is another potential distinguisher.
We have seen how \meek\ tends to use one long-lived connection
through which it tunnels all its requests.
Figure~\ref{fig:concurrent} compares the number of concurrent HTTPS connections to
Google per client in both traces.
The number of connections in the \lbl trace is variable,
with some hosts briefly spiking up above 50 connections,
\vp{Characterize in terms of distinct clients/IP~addresses, too}
but the average case is very heavily skewed to smaller numbers.
The average number of connections in the \lbl trace is 2.61,
with 28\% of clients never having more than 2 concurrent connections.
In the \meek trace the average is almost exactly 1, only briefly
deviating when one connection ends and another begins.
We conclude that having a small number of concurrent connections is unremarkable.
\vp{Could more explicitly frame this in terms of opportunity rather than
just that it's unremarkable}

@@

For the purposes of censorship circumvention,
one does not need to match exactly a ``typical'' traffic profile;
\vp{should discuss the theoretical threat of ``constellation'' attacks,
i.e., where the censor concludes that the overall collective pattern
of a user smells funny [not a threat that actually matters in practice!]}
only not to deviate from it too much.
Circumvention traffic must only be difficult enough to distinguish from ordinary traffic
that blocking it requires an amount of false positives unacceptable to the censor.
Even 1\% of Google traffic accidentally blocked may exceed the collateral damage tolerance of some censors.
Further, it is hard to characterize what normal use is of, say, a CDN:
they provide access to ordinary web sites,
but also to video streams and software updates,
and not all clients are web browsers.
The difficulty we face is symmetric;
if finding the right model is difficult task for us,
it is also difficult for the censor.
We have seen that censors prefer to use easy classifiers when they exist.
\vp{This observation isn't backed up in the paper [or by citation].}
By removing the easy ways, we increase the censor's cost.

@@

Development on \meek\ as a Tor pluggable transport~\cite{pt} began in January~2014.
For deployment we target
the Tor Browser~\cite{torbrowser},
a customized version of Firefox that is
preconfigured to use a built-in Tor client.
% and patched to defend against application-layer privacy and anonymity threats
% like tracking cookies and web browser fingerprinting.
Tor Browser has an easy interface for selecting pluggable transports.
% ANON
% [Some details of deployment are omitted for anonymous submission.]
% We made a series of experimental releases of Tor Browser featuring \meek,
% releasing the first one on February~18.
% On April~18 we made the first release featuring the browser camouflage
% that is the subject of Section~\ref{sec:browserextension}.
% We announced our releases on Tor development mailing lists,
% whence they were picked up by Tor Weekly News on the Tor blog.
% Our code was merged by the Tor Browser maintainers
% in June and is scheduled for an alpha release,
% still pending as of this writing.

We have so far deployed on three backends:
Google App Engine,
Amazon CloudFront,
and Microsoft Azure.
Figure~\ref{fig:clients-tor} shows the daily average number of concurrent users of \meek.
(A measurement of 500, for example, means that there were on average 500
users of the system at any given time during the day.)
The App Engine backend was established in February;
CloudFront in July;
and Azure in October.
Also in Figure~\ref{fig:clients-tor} is a table of monthly costs for each web service.
The pricing for cloud services is complicated,
depending not only on bandwidth but also on geographical region and other factors.
For example CloudFront charges per request as well as per GB,
and about 54\% of the CloudFront bill for October was for requests.
App Engine charges extra when it has to run multiple instances
of an app's code to cope with load;
about 15\% of October's App Engine bill was for such ``instance hours.''
% These and other cost details are summarized in a mailing list post~\cite{meek-costs-201410}.
The App Engine and CloudFront backends are running on accounts
that provide a limited amount of free bandwidth,
but current use greatly exceeds the free thresholds.
Azure service is being donated and so has not yet cost anything.
The total cost so far has been \$187.13,
but this number is expected to more than double in November and continue to increase.

\begin{figure}
\centering
\includegraphics[width=\linewidth]{clients-meek}
\begin{tabular}{l r r r}
       &App Engine &CloudFront&  Azure \\
\hline
Jan--Jul &  \$2.72 &   \$0.00 & \$0.00 \\
Aug      &  \$1.56 &   \$3.10 & \$0.00 \\
Sep      &  \$4.02 &   \$4.59 & \$0.00 \\
Oct      & \$40.85 & \$130.29 & \$0.00 \\
\hline
total    & \$49.15 & \$137.98 & \$0.00 \\
\end{tabular}
\caption{
Concurrent users of the \meek\ pluggable transport
and month-by-month operational costs.
The total cost to date is \$187.13.
% ANON
% The large increase of users on October~15 coincides with
% the release of Tor Browser~4.0,
% the first release to make meek easily available.
Azure CDN service is currently being donated as part of a research grant.
\vp{It would be valuable to build up some sort of estimate of what it
would cost if you didn't have the grant.}
The user estimates come from the Tor Metrics Portal~\cite{metrics-meek,counting-daily-bridge-users}.
}
\label{fig:clients-tor}
\end{figure}

@@

Domain fronting derives its strength from the
high collateral damage of blocking the domain used for the fronting.
To front through \urll{www.google.com} to App Engine, for example,
is to make a bet that the censor will lack the temerity to block Google.
Different censors will differ in their aversion to collateral damage;
blocking an important service is a costly measure
that harms users not involved in circumvention and perhaps a society's economic well-being,
and not all censors can afford to do it.
The Great Firewall of China took the unprecedented step
of blocking all Google services in June 2014~\cite{cn-google-block,cn-google-block-greatfire},
and has since blocked certain CDN domains that were used to host
mirrors of censored web sites, even at the cost of damaging other unrelated sites~\cite{cn-edgecast-block-greatfire}.
In 2012, the government of Pakistan blocked all of YouTube
in order to restrict access to one video,
and in 2011, the government of Egypt briefly completely ``turned off the net.''
% http://www.washingtonpost.com/business/economy/youtube-blocked-in-pakistan/2012/09/17/30081fa2-00ea-11e2-b257-e1c2b3548a4a_story.html
% https://en.wikipedia.org/wiki/Internet_censorship_in_Egypt#2011_Internet_shutdown
These examples show that blocking resistance is not an absolute,
black-and-white security property;
it can only be discussed in an economic context, relative to the costs borne
by the censor and by users of a system.
We can at least roughly quantify the cost of blocking a domain-fronting system:
it is the minimum cost of:
blocking the front domain with resultant collateral damage;
conducting a traffic-analysis attack to distinguish
circumvention from ordinary traffic; or
conducting some other unconsidered attack, for example physical surveillance of Internet users.
As long as all these costs are high,
domain fronting is difficult to block.

A censor could attack domain fronting by
going directly to the operators of the intermediate web service
and asking them either to break fronting
(i.e., require SNI to be present and SNI and Host header to agree),
or to get rid of their customers who are
engaged in enabling circumvention (e.g.,~us).
The censor could threaten to block the web service entirely otherwise.
Whether the attack will succeed depends on the censor's
and the web service's specific costs and motivations,
so we cannot make any general statements.
It is ultimately a question of who needs whom more:
whether it hurts the web service or the censor more
when the service is blocked.
% Nothing works against a censor with sufficiently high tolerance for
% collateral damage,
% but we also do not have to defeat the world's
% most powerful censor in order to be successful.
% What does not work in one place may work in another.
